BurgerMax Presents: OpenAdcess

### 2017-03-01 future-work.tex
Took a stab at the intro
Hecka citations

\section{Future Work}
This future work appears in SIGTBD \todo{citation to future
paper edition}.

@@

\subsection{Future Work}
A consequence of the invention of time travel \todo{Cite paper} and the vanity
of engineers (not scientests) \todo{Cite ubiquity article} is that people
keep going further back in time to give themselves credit for the invention of
the time machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing missadventuresduring our fieldtrip into the past can
be seen here: \todo{Citation to future article: 1984 esque ACM IS EVERYWHERE,
ACM IS UBIQUITY, WE LOVE ACM}
ubiquity paper}

>>>>

\section{Future Work}
\label{sec:future}
This future work appears in SIGTBD \todo{citation to future
paper edition}.

@@

\subsection{Future Work}
A consequence of the invention of time travel \cite{time-travel} and the vanity
of engineers (not scientests) \todo{Cite ubiquity article} is that people
keep going further back in time to give themselves credit for the invention of
the time machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing missadventuresduring our fieldtrip into the past can
be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.

### 2017-03-01 introduction.tex
Hecka citations

\section{Introduction}
Open access is a movement to make papers and other research contributions free
accessible to the general public \todo{cite}.
The ACM has been working for some time to achieve the open access dream but
have found the dream to be prohibitively expensive \todo{cite}.
To fund this venture, we have chosen to adopt the techniques employed by
various other websites and publications that manage to distribute content for
free.

>>>>

\section{Introduction}
Open access is a movement to make papers and other research contributions free
accessible to the general public \cite{oa}.
The ACM has been working for some time to achieve the open access dream but
have found this dream to be prohibitively expensive.
As such, we have required authors to opt-in to open access by paying the cost
themselves \todo{cite (and archive current authors.acm.org page)}.
However, we have found a way to provide open access papers at no cost to the
authors by adopting the techniques employed by various other websites and
publications that manage to distribute content for free.

### 2017-03-01 paper-sponsorships.tex
Hecka citations

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/law-kid-ad.png}
\caption{Get your settlement today! \todo{attribution}}
\label{fig:law}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.95\textwidth]{figures/usa-ad.png}
\caption{We have near absolute power over you! \todo{attribution}}
\label{fig:usa}
\end{figure*}

@@

During each Call for Papers we will also put out a simultaneous Call for
Logos during which companies bid on which letter they want.
We require that the company logo is a stylized version of the letter being
replaced to avoid a Wingdings situation \todo{Cite NYC controversy}.

@@

\paragraph{Overclock}
Overclock is a section for performance enhancing drugs tailored for computer
scientists.
This section is mostly targeted to the Hacker News crowd who exclaims the
benefits of small amounts of LSD for enhancing productivity at work
\todo{cite}.
Although we can't promote the use of illegal drugs our editor is so strung out
on ``road cheese" that she won't notice.
% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/law-kid-ad.png}
\caption{Get your settlement today \cite{med-scale}!}
\label{fig:law}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.95\textwidth]{figures/usa-ad.png}
\caption{We have near absolute power over you \cite{eagle, kanye, microwave}!}
\label{fig:usa}
\end{figure*}

@@

During each Call for Papers we will also put out a simultaneous Call for
Logos during which companies bid on which letter they want.
We require that the company logo is a stylized version of the letter being
replaced to avoid a Wingdings situation \cite{wingdings}.

@@

\paragraph{Overclock}
Overclock is a section for performance enhancing drugs tailored for computer
scientists.
This section is mostly targeted to the Hacker News crowd who exclaims the
benefits of small amounts of LSD for enhancing productivity at work
\cite{microdose, lsd-song}.
Although we can't promote the use of illegal drugs our editor is so strung out
on ``road cheese" that she won't notice.
% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d
